Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-15 automatica/paper.tex
introduction to the cegis for control sec
sec 3

%\author[Paestum]{Marcus Tullius Cicero}\ead{cicero@senate.ir},    % Add the 
%\author[Rome]{Julius Caesar}\ead{julius@caesar.ir},               % e-mail address 
%\author[Baiae]{Publius Maro Vergilius}\ead{vergilius@culture.ir}  % (ead) as shown

%\address[Paestum]{Buckingham Palace, Paestum}  % Please supply                                              
%\address[Rome]{Senate House, Rome}             % full addresses
%\address[Baiae]{The White House, Baiae}        % here.

\begin{keyword}                           % Five to ten keywords,  
Digital Control; A/D converters; Control System Synthesis; Safety Analysis; Quantization Errors; Sampling.               % chosen from the IFAC 
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

\textcolor{red}{[Where are we defining the specifications/properties of interest?]}

\textcolor{red}{[Where are the specifics of the errors due to discretisation/quantisation discussed?]}

@@

%-------------------------------
\subsection{Counterexample Guided Inductive Synthesis} 
\label{ssec:cegis}
%-------------------------------

@@

The input specification provided to CEGIS is of the form
$\exists P .\, \forall a.\, \phi(a, P)$, where $P$ ranges over functions
(where a function is represented by the program computing it),
$a$ ranges over ground terms, and $\phi$ is a quantifier-free formula. 
We~interpret the ground terms over some finite domain~$\mathcal{D}$.
%

The design of our synthesizer consists of two phases, an inductive
synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of test vectors {\sc
  inputs} that is updated incrementally.  Given the aforementioned
specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.

@@

%-------------------------------
\subsection{Naive approach} 
\label{sssec:naive}
%-------------------------------

>>>>

\begin{keyword}                           % Five to ten keywords,  
Digital control synthesis; Safety requirements; A/D converters; Quantization errors; Sampling.               % chosen from the IFAC 
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

%-------------------------------
\subsection{\textcolor{red}{[Elizabeth: please add the specifics of the errors due to discretisation/quantisation, with reference to Fig. \ref{fig:digitalsystem}]}}
%\label{sec:}
%-------------------------------

@@

%-------------------------------
\subsection{Counterexample Guided Inductive Synthesis - CEGIS} 
\label{ssec:cegis}
%-------------------------------

@@

We consider an input specification of the form $\exists P .\, \forall a.\, \phi(a, P)$, 
where $P$ ranges over functions (where a function is represented by the program computing it),
$a$ ranges over ground terms, 
and $\phi$ is a quantifier-free formula. 
We~interpret the ground terms over some finite [CHECK: finite? are we doing only SAT or also SMT?] domain~$\mathcal{D}$. 
This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms. 
CEGIS breaks down this generally hard synthesis problem into two easier parts.

The design consists of two phases, an inductive synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of tests {\sc
  inputs} that is updated incrementally.  Given the specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.
[COMMENT ON TERMINATION?]

@@

In this section we discuss two instantiations of CEGIS: the first,
na\"ive one, relies on an unfolding of the dynamics up to a
completeness threshold, while the second one is abstraction-based and
leverages abstraction refinement and acceleration to improve
scalability while retaining soundness.

%-------------------------------
\subsection{Na\"ive approach} 
\label{sssec:naive}
%-------------------------------
